|

### 2019-08-29 paper.Rmd
Added simulation, trying to work out whats wrong.

@@

XXXX not sure this makes sense, need to check against plots (not what I was expecting, need to think about this more)
Best guess is that relation between $\phi$ and $h$ only holds for 3d sphere, how can I generalise it?

>>>>

XXXX maybe the problem is that each plane is 2d, but the cap assumes I am cutting with a hyperplane that is n-1, so it works as expected in 3d, beyond that i need to account for volume effects in the n-2 dimensions, but how?
e.g. consider 1-d sliced of 3d sphere, in that case I get the volume of the slice as a pipe of radius h, so for n-d sphere I need the volume of n-1 d sphere of radius h but translated across the plane (but what does that really mean)?

@@
